\documentclass[letterpaper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{
    a4paper,
    top=1in,
    bottom=1in,
    left=1in,
    right=1in,
    headheight=0pt,
    headsep=0pt,
    footskip=0pt
}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    citecolor=black,
    filecolor=black,
    menucolor=black,
    runcolor=black
}
\usepackage{titlesec}

\titleformat{\section}{
  \vspace{-1em}\normalfont\Large\bfseries\color{black}
}{}{0em}{\MakeUppercase}
[\titlerule]

\newcommand{\resumeitem}[1]{
    \item \small #1
}

\newcommand{\resumesubheading}[4]{
    \vspace{-0.5em}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-0.5em}
}

\newcommand{\resumesubsubheading}[2]{
    \vspace{-0.5em}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-0.5em}
}

\newcommand{\resumesubsubitem}[1]{
    \item \small #1
}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\Huge\textbf{Dhruvil Gajjar}} \\
    \vspace{0.1em}
    \textbf{Frontend Engineer} \\
    \vspace{0.2em}
    \small
    +919512531333 \textperiodcentered\ dgajjar999@gmail.com \textperiodcentered\ \href{https://dhruvilgajjar.netlify.app}{dhruvilgajjar.netlify.app} \textperiodcentered\ \href{https://github.com/whodhruvil}{GitHub} \textperiodcentered\ \href{https://www.linkedin.com/in/dhruvil-gajjar}{LinkedIn}
\end{center}

\section*{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small
    \textbf{Frontend Development:} React.js, Redux, JavaScript, TypeScript, HTML5, CSS3, SCSS, Tailwind CSS, Styled Components, Webpack, Next.js, Material UI, Bootstrap, jQuery, React Native, Expo
    \item \small
    \textbf{State Management:} Redux, Context API, Hooks
    \item \small
    \textbf{Backend Knowledge:} REST APIs, GraphQL, Node.js, Express, NestJS, PHP
    \item \small
    \textbf{Tooling \& Deployment:} Git, CI/CD, Figma, Storybook, Sentry, Jest, React Testing Library, Bundle Analyzer
    \item \small
    \textbf{Other:} Problem-Solving, Logical Reasoning, OOPs, Agile Development
\end{itemize}

\section*{Work Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumesubheading{Bacancy}{Ahmedabad, India}
    {\textit{Sr. Software Engineer}}{March 2025 \textemdash PRESENT}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{Engineered the frontend architecture for a real-time IoT vehicle tracking platform, enabling live location monitoring and comprehensive commute data visualization.}
        \resumeitem{Improved application performance by \textbf{98\%}, reducing load times from 3 minutes to 2 seconds for heavy telemetry datasets by optimizing rendering and data processing pipelines.}
        \resumeitem{Spearheaded the client-side architectural migration from Traccar to Flespi, ensuring seamless data integration and enhancing overall system scalability.}
        \resumeitem{Built dynamic analytical dashboards featuring custom trip and stop calculators, delivering granular reports on exact locations, timestamps, average speeds, and route metrics.}
        \resumeitem{\textit{Technology Stack:} JavaScript, TypeScript, React, Redux, Jest, Tailwind CSS}
    \end{itemize}

    \resumesubheading{Saleshandy (SaaS)}{Ahmedabad, India}
    {\textit{Software Engineer}}{October 2021 \textemdash January 2025}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{Spearheaded the development of a billing system using React and Stripe, reducing payment errors by \textbf{25\%} for 3,000+ users.}
        \resumeitem{Enhanced user onboarding by \textbf{30\%} and retention by \textbf{15\%} by implementing plan-based restrictions and trial features.}
        \resumeitem{Reduced frontend development time by \textbf{60\%} across 3+ products by architecting a reusable React component library, ensuring 100\% UI/UX consistency.}
        \resumeitem{Automated CI/CD pipelines for the component library, enabling \textbf{100\%} auto-deployments on NPM with seamless versioning.}
        \resumeitem{Engineered interactive analytics reports using ApexCharts, delivering up to \textbf{50\%} faster insights and enhancing user engagement by \textbf{20\%}.}
        \resumeitem{Optimized build processes by integrating Bundle Analyzer to identify large packages and reduce bundle size.}
        \resumeitem{Improved application performance and reduced load time by implementing Web Workers for offloading intensive tasks to background threads.}
        \resumeitem{Demonstrated backend development capabilities by building simple CRUD REST APIs using NestJS, contributing to full-stack project success.}
        \resumeitem{\textit{Technology Stack:} TypeScript, JavaScript, ReactJS, Stripe, Redux, HTML, CSS, SCSS, NestJS, Figma, Jest, React Testing Library}
    \end{itemize}

    \resumesubheading{Codrain Technolabs Pvt Ltd.}{Ahmedabad, India}
    {\textit{Software Engineer}}{January 2020 \textemdash October 2021}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{Crafted efficient, scalable mobile applications using JavaScript, React Native, and Redux, contributing to enhanced user experiences and system reliability.}
        \resumeitem{Designed and built WalkMapper, a mobile application for Android and iOS, serving over \textbf{10,000+} residents in the New York area to report public issues.}
        \resumeitem{Facilitated streamlined reporting of public issues, including non-functional streetlights, uncleared snow, and faulty traffic signals, enabling a \textbf{30\%} faster response rate from government authorities and improving community safety.}
        \resumeitem{\textit{Technology Stack:} JavaScript, React, React Native, Expo, Redux}
    \end{itemize}
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumesubheading{Gyanmanjari Innovative University}{Bhavnagar, India}
    {\textit{Bachelor of Engineering - INFORMATION TECHNOLOGY}}{August 2016 \textemdash August 2020}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{CGPA: 8.38 / 10.0}
    \end{itemize}
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumesubsubheading{FakeTwitter}{}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{Developed a Twitter-like platform with features for posting, liking, and commenting on tweets using React.js, Semantic UI, Apollo Client, Node.js, MongoDB, and GraphQL via Apollo Server.}
    \end{itemize}
    \resumesubsubheading{iMovie}{}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{Developed an interactive movie library website using Next.js, Tailwind CSS, and the TMDB API, featuring over \textbf{1,500+} films organized by genre, enhancing user engagement.}
    \end{itemize}
    \resumesubsubheading{GeekyBot}{}
    \begin{itemize}[leftmargin=0.15in, label={$\cdot$}]
        \resumeitem{Developed a voice-command news web application utilizing React, Material UI, and Alan AI for seamless voice interaction; integrated NEWSAPI.org to deliver real-time updates with \textbf{90\%} accuracy in content delivery.}
    \end{itemize}
\end{itemize}

\end{document}